Yoghurt under stress

### 2014-06-28 plis_beamer.tex
lighter version of the XYslices
Add videos for carpet and flying carpet case Re-work conclusion to fit in the "mechanics of biogels" theme

	\node[minimum width = 0.156\textwidth, minimum height=0.156\textwidth, anchor=north west, draw=Accent1] at ($(c.north west) + (0.125\textwidth,0)$) (dz) {};
	\draw[ultra thick] (c.south east) ++(0,-0.25em) -- ++(-0.132\textwidth,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
\end{tikzpicture}
}{volume_plis.avi}
\end{frame}

@@

	\includegraphics[width=\textwidth]{volume_cloque_t116}\\
	\begin{tikzpicture}
	\draw[ultra thick] (0,) -- +(0.786\textwidth,0) node[midway, below] {\SI{1}{\milli\metre}};
	\end{tikzpicture}

@@

\begin{frame}{Viscosity of the solvent during gel formation}
\begin{tabu}{X[c]X[c]}
water, $\eta=\SI{1}{\milli\pascal\second}$ &
glycerol 60\%, $\eta=\SI{10}{\milli\pascal\second}$\\
\includegraphics[width=0.45\textwidth]{XYslice_gly0}&
\includegraphics[width=0.45\textwidth]{XYslice_gly60}
\end{tabu}
\tikz\draw[line width=0.2em] (0,0) -- ++(0.045\textwidth,0) node[midway, below] {\SI{10}{\micro\metre}};
\end{frame}

\begin{frame}{Conclusion}
Spontaneous wrinkling of over-acidified casein gels in non-adhesive confinement

	\structure{Original patterns}
	\begin{itemize}
		\item nested (optical elements ?)
		\item kinetic wavelength selection
	\end{itemize}
	\structure{A new wrinkling mechanism}
	\begin{itemize}
		\item porous flow resist bending
		\item Darcy can beat Poiseuille
		\item may extend to other porous sheets (wet paper, biological membranes\ldots)
	\end{itemize}
	\structure{Viscosity influences}
	\begin{itemize}
		\item porous dissipation
		\item gel formation (theory?)
		\raisebox{0.6\normalbaselineskip}[0pt][0pt]{$\left.\rule{0pt}{1.1\normalbaselineskip}\right\}$ thus wrinkling}
	\end{itemize}
	\structure{To do:} Measure everything to plot $\lambda_\text{theory}$ vs $\lambda_\text{experiment}$
\end{frame}

>>>>

	\node[minimum width = 0.156\textwidth, minimum height=0.156\textwidth, anchor=north west, draw=Accent1] at ($(c.north west) + (0.125\textwidth,0)$) (dz) {};
	\draw[ultra thick] (c.south east) ++(0,-0.25em) -- ++(-0.132\textwidth,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
\end{tikzpicture}
}{volume_plis_comp.avi}
\end{frame}

@@

	\movie[externalviewer]{\includegraphics[width=\textwidth]{volume_cloque_t116}{volume_cloques_comp.avi}\\
	\begin{tikzpicture}
	\draw[ultra thick] (0,) -- +(0.786\textwidth,0) node[midway, below] {\SI{1}{\milli\metre}};
	\end{tikzpicture}

@@

\begin{frame}{Viscosity of the solvent during gel formation}
\begin{tabu}{X[c]X[c]}
water, $\eta=\SI{1}{\milli\pascal\second}$ &
glycerol 60\%, $\eta=\SI{10}{\milli\pascal\second}$\\
\includegraphics[width=0.45\textwidth]{XYslice_gly0.jpg}&
\includegraphics[width=0.45\textwidth]{XYslice_gly60.jpg}
\end{tabu}
\tikz\draw[line width=0.2em] (0,0) -- ++(0.045\textwidth,0) node[midway, below] {\SI{10}{\micro\metre}};

\structure{To do:} Measure everything to plot $\lambda_\text{theory}$ vs $\lambda_\text{experiment}$
\end{frame}

\begin{frame}{Solvent is important in biogel mechanics}

\structure{Gel formation}
\begin{itemize}
	\item non adhesive boundary conditions $\Rightarrow$ synæresis
	\item gel properties depend on solvent viscosity
\end{itemize}

\bigskip
\structure{Non monotonic $p$H dependence}
\begin{itemize}
	\item spontaneous re-swelling $\Rightarrow$ biaxial compression
	\item lateral confinement $\Rightarrow$ cascade buckling, nested structures.
\end{itemize}

\bigskip
\structure{Gel poroelasticity}
\begin{itemize}
	\item porous flow resist bending
	\item Darcy can beat Poiseuille
\end{itemize}

\end{frame}
